---
title: "Portfolio 3"
author: "Tahmain Akther Monisa"
date: "2024-04-26"
output: html_document
---

**Load the dataset**

```{r}
data <- read.csv("C:/miami-housing.csv")
head(data)
str(data)
summary(data)
data$LATITUDE<-NULL
data$LONGITUDE<-NULL
data$avno60plus<-NULL
head(data)
```
**splitting the data into training (70%) and testing (30%) sets**
```{r}
sample_size <- floor(0.7*nrow(data))
train_index <- sample(seq_len(nrow(data)), size = sample_size)
train <- data[train_index, ]
test <- data[-train_index, ]

View(train)
View(test)
```

**Fitting the model on the training data**

```{r}
lm_model <- lm(SALE_PRC~RAIL_DIST+CNTR_DIST+month_sold, data=train)
summary(lm_model)
```

**Making prediction on the testing set **

```{r}
lm_predictions <- predict(lm_model, newdata = test)
chooseCRANmirror(ind=1) # This opens a window where you can select a CRAN mirror
install.packages("caret")
library(caret)
lm_performance<- postResample(pred = lm_predictions, obs = test$SALE_PRC)
print(lm_performance)
```

**Implementing Decision Tree model **

```{r}
install.packages("e1071")
library(e1071)
library(rpart)
dt_model <- svm(SALE_PRC~RAIL_DIST+CNTR_DIST+month_sold, data=train)
dt_prediction <- predict(dt_model, newdata = test)
dt_performance <- postResample(pred = dt_prediction, obs = test$SALE_PRC)
print(dt_performance)

```

**Implementing a SVR Model (Poly Kernel) **
```{r}
svr_linear <- svm(SALE_PRC~RAIL_DIST+CNTR_DIST+month_sold, data = train, kernel="poly")
svr_linear_prediction <- predict(svr_linear, newdata=test)
svr_performance <- postResample(pred = svr_linear_prediction, obs = test$SALE_PRC)
print(svr_performance)
```
**Implementing a SVR Model(Radial kernel)**
```{r}
svr_linear <- svm(SALE_PRC~RAIL_DIST+CNTR_DIST+month_sold, data = train, kernel="radial")
svr_linear_prediction <- predict(svr_linear, newdata=test)
svr_performance <- postResample(pred = svr_linear_prediction, obs = test$SALE_PRC)
print(svr_performance)
```

**Implementing a SVR Model (Linear Kernel) **
```{r}
svr_linear <- svm(SALE_PRC~RAIL_DIST+CNTR_DIST+month_sold, data = train, kernel="linear")
svr_linear_prediction <- predict(svr_linear, newdata=test)
svr_performance <- postResample(pred = svr_linear_prediction, obs = test$SALE_PRC)
print(svr_performance)
```
**Implementing Random Forest Model (n100)**

```{r}
install.packages("randomForest")
library(randomForest)
rf_model_n100 <- randomForest(SALE_PRC~RAIL_DIST+CNTR_DIST+month_sold, data=train, ntree=100)
rf_predictions_n100<- predict(rf_model_n100,newdata = test)
rf_performance_n100<- postResample(pred = rf_predictions_n100,obs = test$SALE_PRC)
print(rf_performance_n100)

```

**Implementing Random Forest Model (n200)**
```{r}
rf_model_n200 <- randomForest(SALE_PRC~RAIL_DIST+CNTR_DIST+month_sold, data=train, ntree=200)
rf_predictions_n200<- predict(rf_model_n200,newdata = test)
rf_performance_n200<- postResample(pred = rf_predictions_n200,obs = test$SALE_PRC)
print(rf_performance_n200)

```
**Implementing Random Forest Model (n500)**
```{r}
rf_model_n500 <- randomForest(SALE_PRC~RAIL_DIST+CNTR_DIST+month_sold, data=train, ntree=500)
rf_predictions_n500<- predict(rf_model_n500,newdata = test)
rf_performance_n500<- postResample(pred = rf_predictions_n500,obs = test$SALE_PRC)
print(rf_performance_n500)
```

**Drawing a barchart to find best model for the created model**
```{r}
Models <- c(2.932007, 2.903009, 3.047220, 2.903009, 3.042950, 2.696247, 2.683682, 2.686284)
models_names <- c("LM_Model","DT_Model", "SVR_Poly", "SVR_Radial", "SVR_Linear", "RF_n100", "RF_n200", "RF_n500")

barplot(Models,
        main = "Error matrics RMSE",
        xlab = "Models",
        ylab = "RMSE",
        names.arg = models_names
)
```
